`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-16 inst/manuscript/manuscript.rmd
Integrate new data from Birgit Ploier;

`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
step plots the corresponding spectral traces (Figure 1). Note that algorithmic
alignment to the time of dithionite addition is employed (default) as well as 
custom trimming of the time axis to account for divergent acquisition 
times between experiments. PPR scaling is used with the default factor of 0.65.

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 2A)
scramblase_assay_plot(
  "inputTable.txt") +
xlim(0, 2)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 2B)
scramblase_assay_plot(
  "inputTable.txt",
  split_by_experiment = FALSE) + 
xlim(0, 2)
```

>>>>

`flippant`s capabilities are demonstrated here by reanalyzing a subset of the
data underlying  Figure 4C--F in @ploier_dimerization_2016. The following work
flow in a first  step plots the corresponding spectral traces (Figure 1). Note
that algorithmic alignment to the time of dithionite addition is employed
(default) as well as  custom trimming of the time axis to account for divergent
acquisition  times between experiments. PPR scaling is used with the default
factor of 0.65.

@@

```{r noeval_demonstrate_plot, eval = FALSE}
# Plot PPR plot (Figure 2A)
scramblase_assay_plot(
  "inputTable.txt") +
xlim(0, 3)
```

@@

```{r noeval_demonstrate_plot2, eval = FALSE}
# Plot PPR plot (Figure 2B)
scramblase_assay_plot(
  "inputTable.txt",
  split_by_experiment = FALSE) + 
xlim(0, 3)
```
